\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}

\title{Hybrid Upper Body Workout \\ \large Strength + Hypertrophy}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Workout Overview}
\textbf{Goal:} Develop strength in foundational lifts while adding hypertrophy volume to sculpt detail and balance. \\
\textbf{Duration:} 75--90 minutes \\
\textbf{Structure:} Heavy compound lifts (Strength Block) + Isolation accessory work (Hypertrophy Block)

\vspace{1em}
\section*{Guidelines}
\begin{itemize}[leftmargin=1.5em]
  \item \textbf{Strength Block:} 3--6 reps, RPE 8.5--9, 2.5--4 min rest
  \item \textbf{Hypertrophy Block:} 8--15 reps, RPE 8, 45--75 sec rest
  \item \textbf{Tempo:} 2--3 sec eccentric, controlled concentric
  \item \textbf{Warm-up:} Mobilize shoulders, wrists, upper back; perform 2–3 warm-up sets per compound lift
\end{itemize}

\vspace{1em}
\section*{1. Strength Block}

\begin{itemize}[leftmargin=1.5em]
  \item \textbf{Barbell Overhead Press} \\
    \textit{Sets: 4 \quad Reps: 4--6 \quad RPE: 9} \\
    Primary Movers: Anterior deltoids, triceps \\
    \textit{Cue: Engage core and glutes; bar path should stay close to face.}
    
  \item \textbf{Weighted Pull-Ups (or Heavy Lat Pulldown)} \\
    \textit{Sets: 4 \quad Reps: 5--6 \quad RPE: 9} \\
    Primary Movers: Lats, biceps, rhomboids \\
    \textit{Cue: Pull chest to bar, avoid swinging.}

  \item \textbf{Flat Barbell Bench Press} \\
    \textit{Sets: 4 \quad Reps: 3--5 \quad RPE: 9} \\
    Primary Movers: Pectoralis major, anterior deltoids, triceps \\
    \textit{Cue: Retract scapula, lower with control, drive with full-body tension.}
\end{itemize}

\vspace{1em}
\section*{2. Hypertrophy Block}

\begin{itemize}[leftmargin=1.5em]
  \item \textbf{Incline Dumbbell Press} \\
    \textit{Sets: 3 \quad Reps: 8--10 \quad RPE: 8} \\
    Target: Upper chest \\
    \textit{Cue: Set bench to 30--45°, stretch at bottom, control the press.}

  \item \textbf{Cable Lateral Raises} \\
    \textit{Sets: 3 \quad Reps: 10--12 \quad RPE: 8} \\
    Target: Lateral deltoid \\
    \textit{Cue: Lead with elbow, avoid shrugging, maintain constant tension.}

  \item \textbf{Dumbbell Rear Delt Fly} \\
    \textit{Sets: 3 \quad Reps: 10--15 \quad RPE: 8} \\
    Target: Rear deltoid, rhomboids \\
    \textit{Cue: Hinge at hips, keep neck neutral, squeeze scapula at top.}

  \item \textbf{Alternating Dumbbell Bicep Curls} \\
    \textit{Sets: 3 \quad Reps: 8--12 \quad RPE: 8} \\
    Target: Biceps brachii \\
    \textit{Cue: Elbows stay tucked, emphasize slow negative phase.}

  \item \textbf{Rope Tricep Pushdowns} \\
    \textit{Sets: 3 \quad Reps: 10--12 \quad RPE: 8} \\
    Target: Triceps \\
    \textit{Cue: Spread rope at bottom, pause with full extension.}
\end{itemize}

\vspace{1em}
\section*{Optional Finisher}
\textbf{Push-up to Failure $\rightarrow$ Plank Hold (60s) $\rightarrow$ Rest 2 min, Repeat x2} \\
Goal: Burnout + Core Engagement

\vspace{1em}
\section*{Post-Workout}
\begin{itemize}[leftmargin=1.5em]
  \item Protein: 30--40g + Carbohydrates to replenish glycogen
  \item Hydration: At least 750ml water post-session
  \item Recovery: 7–9 hours sleep; consider magnesium before bed
\end{itemize}

\end{document}
